\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2015-02-27 paper2015asml.tex

Recent work has also addressed the task of making motions predictable (similar motions in similar environments and tasks) and/or legible (make it easier for human observers to understand the intent of the robot)~\cite{Beetz:2010}. Legibility makes it possible for human observers to understand clearly what a robot is intending to do, allowing them to modify their actions and motions if necessary. Predictability implies that the robot will always be consistent in its actions, removing the element of surprise for human observers. These concepts have been well-studied recently with the intent of measuring legibility~\cite{Lichtenthaler:2011}, using expressions to improve the readability of robots~\cite{Takayama:2011} and generating anticipation~\cite{Gielniak:2011}. In~\cite{Dragan:2013}, the notion of legibility was incorporated into a constrained trajectory optimization motion planner to generate motions that are more legible to human observers,\hl{ while in}~\cite{mainprice2011planning} \hl{a cost-map was developed in conjunction with sampling based planning to produce trajectories in cluttered ienvironements.}

@@

The planning algorithms that we used are RRT-Connect~\cite{kuffner2000rrt} and RRT*.  RRT*~\cite{frazzoli-RRTstar} was used with two different cost functions: PathLength and MaxMinClearance.The objective for PathLength minimizes the length of the trajectory (as the sum of the euclidean distances between ends of trajectory segments). The objective for MaxMinClearance computes uses the minimum clearance of a configuration belonging to a trajectory as the value it is trying to maximize. Both planners are implemented in the OMPL library~\cite{OMPL:2012}. All the paths generated by RRT-Connect are shortcutted for a finite amount of time to improve the quality of the paths. The planned trajectories are post-processed by an iterative-time parameterization method that time-parameterizes the trajectories while taking into account velocity and accelerations. The infrastructure we designed around MoveIt! allows us to automatically generate movies of the generated trajectories using the ROS Visualizer (Rviz). We generated movies from different viewpoints to maximize the visibility of the motion to human observers reviewing it. A total of 103 different trajectories were generated in this manner.

@@

We conducted an online survey\footnote{The online survey was conducted after gaining a waiver from SRI's IRB after a review of our survey procedure. Our survey followed standard guidelines for privacy of respondent information when conducting a survey on Mechanical Turk.} where we asked human observers to rate a variety of trajectories of the PR2 robot. The survey was built on Amazon's Mechanical Turk, which has become a useful tool for large online data gathering and crowd-sourced work. Each respondent in the survey was presented with a set of demographic questions, a video, and asked to rate the robot's motion on the attributes  of elegance, efficiency, smoothness and overall impression (a summary of the rating scales used in the main survey question can be seen in Table~\ref{tab:rating_scales}). The ratings were later converted into numerical values on a scale of 1 to 7. Each respondent was expected to rate multiple trajectories but could not rate a trajectory more than once. Each video has four different views of the robot displayed simultaneously. Respondents were asked demographic questions about familiarity with video games, familiarity with robotics, age group and highest education level. The demographic information was not used to filter the responses we collected.

@@

We identified and computed multiple types of trajectory features. This set of features were selected to characterize the trajectories that were produced for the purpose of identifying the most informative sub-set. Developing a larger variety of more complicated and descriptive features is left as an avenue for future work.

@@

{\bf Joint Limit Distance: }
The maximin distance to joint limits is the maximum over waypoints, of the miniminum over joints of their distance to their respective closest limit (upper or lower), or $\max_{q \in \tj{}} \min_{\theta \in q} \min(|\theta-\theta_U|,|\theta-\theta_L|)$.

@@

In all, we utilized three different classification frameworks to predict overall ratings - decision trees, random forests and boosting. As a base framework we first construct a decision tree model.  Decision trees for classification provide a good visual representation especially in the presence of complex features, where the relationships between predictors and response is not immediately obvious. The features of interest in the first decision tree that we derived include the DTW distance computed for the wrist (vs. the tool path) denoted by wrist\_tool\_dtw, the Hausdorf distance computed for the end-effector and the max curvature computed for the elbow. Using 10-fold cross-validation, we also design a simpler tree that has just three terminal nodes with the wrist\_tool\_dtw feature serving as the key discriminant among the classes. This tree has an accuracy of 86\% on the test data. Large values of the wrist\_tool\_dtw feature correspond to extra rotations of the wrist as the tool is moving towards the goal - such trajectories are rated as low quality by the human observers.

@@

The dataset we have collected and the analysis we have already done in this paper will serve as a
 platform for further development of the idea of using 
a data-driven approach to motion planning. We intend to attempt to learn a cost function for describing the relation between the features and 
the ratings of the generated trajectories using inverse reinforcement learning. We hope to examine whether a cost function derived in this manner will 
lead to generation of more preferred trajectories. We would also like to extend our set of features to include more dynamic features to capture the effect 
that the dynamics of the motions have on the perception of the motion. \hl{Moreover, the feature set we describe in the paper should grow to further describe the spatial motions even more.} The infrastructure that we have developed for generating and conducting 
surveys is fairly generic and could easily be extended to surveying people using trajectories from real robots. This is another avenue we intend to explore 
in the near future. We also intend to explore the potential for open-sourcing the data and infrastructure to allow other researchers to conduct surveys of their own.

>>>>

Recent work has also addressed the task of making motions predictable (similar motions in similar environments and tasks) and/or legible (make it easier for human observers to understand the intent of the robot)~\cite{Beetz:2010}. Legibility makes it possible for human observers to understand clearly what a robot is intending to do, allowing them to modify their actions and motions if necessary. Predictability implies that the robot will always be consistent in its actions, removing the element of surprise for human observers. These concepts have been well-studied recently with the intent of measuring legibility~\cite{Lichtenthaler:2011}, using expressions to improve the readability of robots~\cite{Takayama:2011} and generating anticipation~\cite{Gielniak:2011}. In~\cite{Dragan:2013}, the notion of legibility was incorporated into a constrained trajectory optimization motion planner to generate motions that are more legible to human observers,\hl{ while in}~\cite{mainprice2011planning} \hl{a cost-map was developed in conjunction with sampling based planning to produce trajectories in cluttered environments.}

@@

The planning algorithms that we used are RRT-Connect~\cite{kuffner2000rrt} and RRT*.  RRT*~\cite{frazzoli-RRTstar} was used with two different cost functions: PathLength and MaxMinClearance.The objective for PathLength minimizes the length of the trajectory (as the sum of the euclidean distances between ends of trajectory segments). The objective for MaxMinClearance computes uses the minimum clearance of a configuration belonging to a trajectory as the value it is trying to maximize. Both planners are implemented in the OMPL library~\cite{OMPL:2012}. All the paths generated by RRT-Connect are shortcutted for a finite amount of time to improve the quality of the paths. The planned trajectories are post-processed by an iterative-time parameterization method that time-parameterizes the trajectories while taking into account velocity and accelerations. The infrastructure we designed around MoveIt! allows us to automatically generate movies of the generated trajectories using the ROS Visualizer (Rviz). We generated movies from different viewpoints to maximize the visibility of the motion to human observers reviewing it. A total of 103 different trajectories were generated in this manner. Note that although the planners we use are randomized, the post-processing step (short-cutting) helps significantly in smoothing the plans.

@@

We conducted an online survey\footnote{The online survey was conducted after gaining a waiver from SRI's IRB after a review of our survey procedure. Our survey followed standard guidelines for privacy of respondent information when conducting a survey on Mechanical Turk.} where we asked human observers to rate a variety of trajectories of the PR2 robot. \hl{Our intent with the survey was to get measures of how comfortable the observers were with the generated trajectories.} The survey was built on Amazon's Mechanical Turk, which has become a useful tool for large online data gathering and crowd-sourced work. Each respondent in the survey was presented with a set of demographic questions, a video, and asked to rate the robot's motion on the attributes  of elegance, efficiency, smoothness and overall impression (a summary of the rating scales used in the main survey question can be seen in Table~\ref{tab:rating_scales}). The ratings were later converted into numerical values on a scale of 1 to 7. Each respondent was expected to rate multiple trajectories but could not rate a trajectory more than once. Each video has four different views of the robot displayed simultaneously. Respondents were asked demographic questions about familiarity with video games, familiarity with robotics, age group and highest education level. The demographic information was not used to filter the responses we collected.

@@

We identified and computed multiple types of trajectory features. This set of features were selected to characterize the trajectories that were produced for the purpose of identifying the most informative sub-set. \hl{The selected features measure geometric, dynamic, environment and comparative properties of the trajectories. Since the observed robot was simulated, these visual features seemed to offer the best measures of feedback that the observers might be using in their rating.} Developing a larger variety of more complicated and descriptive features is left as an avenue for future work.

@@

{\bf Joint Limit Distance: }
The maximin distance to joint limits is the maximum over waypoints, of the miniminum over joints of their distance to their respective closest limit (upper or lower), or $\max_{q \in \tj{}} \min_{\theta \in q} \min(|\theta-\theta_U|,|\theta-\theta_L|)$. Note that although the joint limit feature may not be immediately perceived by users, we chose to include it to see if the data might prove otherwise.

@@

\hl{The goal of the classification problem is to predict the overall rating that human observers would assign to a new trajectory based on the observed ratings in the survey.} In all, we utilized three different classification frameworks to predict overall ratings - decision trees, random forests and boosting. As a base framework we first construct a decision tree model.  Decision trees for classification provide a good visual representation especially in the presence of complex features, where the relationships between predictors and response is not immediately obvious. The features of interest in the first decision tree that we derived include the DTW distance computed for the wrist (vs. the tool path) denoted by wrist\_tool\_dtw, the Hausdorf distance computed for the end-effector and the max curvature computed for the elbow. Using 10-fold cross-validation, we also design a simpler tree that has just three terminal nodes with the wrist\_tool\_dtw feature serving as the key discriminant among the classes. This tree has an accuracy of 86\% on the test data. Large values of the wrist\_tool\_dtw feature correspond to extra rotations of the wrist as the tool is moving towards the goal - such trajectories are rated as low quality by the human observers.

@@

The dataset we have collected and the analysis we have already done in this paper will serve as a
 platform for further development of the idea of using 
a data-driven approach to motion planning. We intend to attempt to learn a cost function for describing the relation between the features and 
the ratings of the generated trajectories using inverse reinforcement learning. We hope to examine whether a cost function derived in this manner will 
lead to generation of more preferred trajectories.

\hl{We would also like to extend our set of features in multiple ways. We would like to include more dynamic features to capture the effect 
that the dynamics of the motions have on the perception of the motion. We would also like to introduce more environment specific features, e.g. the descriptors in~\cite{10-jetchev-ICRA}, to account better for the effect of the environment on the ratings. Context and task specific features would be useful in capturing task specific motions, e.g. a robot turning a screwdriver may actually need to turn its wrist continuously. Incorporating task motions and relevant environments, e.g. picking up an object from a cluttered table, would also help in evaluating features like legibility. We would also like to examine how people's ratings change as they spend more time observing the robot (this effort will require a longer running survey or multiple surveys spaced apart in time). We would also like to include features to encode the choice of start and goal positions for the robot - several of the existing features could easily be adapated to take this into account.} The infrastructure that we have developed for generating and conducting 
surveys is fairly generic and could also easily be extended to surveying people using trajectories from real robots. This is another avenue we intend to explore 
in the near future. We also intend to explore the potential for open-sourcing the data and infrastructure to allow other researchers to conduct surveys of their own.
